A robust framework for variable extrusion width concentric toolpath generation

### 2019-08-01 6_validation.tex
clearly introduce functions as belonging to the beading strategy
rewrite beading strategy section and write beading interpolation
rewrite toolpath extraction section
remove combined strategy
formalized all tested strategies

\section{Validation}

@@

\subsection{Strategies}
We can emulate a variety of toolpath generation strategies by applying various beading strategies to our framework.

\paragraph{Naive Strategy}

@@

\paragraph{Deviation at middle}
Emulates \cite{Jin2017}

@@

@@

\paragraph{Combined strategy}
\Cref{wedge_and_infill} shows a combined toolpath strategy.

\begin{figure}
\centering
\includegraphics[width=.99\columnwidth]{sources/method/wedge_and_infill.pdf}
\caption{Use single and double wall lines in regions where the infill would be too thin.}
\label{wedge_and_infill}
\end{figure}

>>>>

\section{Validation}
We use the following constants:
\begin{align}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= \SI{0.4}{\milli\meter} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent}
\end{align}

@@

Our beading strategies are based on a prefered width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.

We set 
\begin{align*}
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

\subsection{Strategies}
We can emulate a variety of toolpath generation methods from related literature by applying various beading strategies to our framework.

\paragraph{Naive Strategy}
Because the naive strategy never employs single line polyline segments, we disable marking edges using the significance measure by choosing the limit angle.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
b(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
b(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Deviating toolpath at center}
Emulates \cite{Jin2017}

$r_\text{min} = 0.8 w_\text{pref}$ and $r_\text{max} = 1.25 w_\text{pref}$

\begin{align*}
b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
b(d) &= b^-(d) +
\begin{cases}
-1 & \text{ if } b^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  b^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

@@

$d_\text{max}^\text{intersection} = \SI{0}{\percent}$

\begin{align*}
t(n) &= 0 \\
b(d) &=
\begin{cases}
1 & \text{ if } d < w_\text{pref} \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w_\text{pref} & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w_\text{pref} / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}

@@

\begin{align*}
b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}
